TODO: title

### 2014-05-05 paper/main.tex
minor work
some very small amout of work.

\section{Introduction}
  % describe new user experience in in recommender systems.
  One of the important problems in recommender systems is the new user experiance.

  % new user experience is important, and here is why.
    % talk about first impressions and user trust
    % How an algorithm behaves the first time a user sees it is important (first impression)
  How a recommender system handels new users can change how these users interact with the recommender system.
%%%%%%%%%%%%%%%%%%%%%%
  The new user experience is a very important part of any recommender system.
  The first interaction with a system is the only chance the system gets to make a first impression on the user.
  This first impression can be very important in structuring a user's expectations for how the system will behave, and determining how much the user trusts the system's recommendations.
  If the system behaves poorly when the user is new, then the user may leave and not come back.
  This is especially a concern with recommender systems which rely on large amounts of user information to make personalization decisions.
  When users are new the system will not have much information to personalize the user experience which may lead the user to leave the system.
%%%%%%%%%%%%%%%%%%%%%%

@@

  %TODO: verify these claims.
  %TODO: check for examples of how to write this
  % algorithm is configured as such.
  %TODO: topic sentence.

  % evaluation and code to run these algortihms available at.
  % citations and lenskit info
  Each algorithm was configured and tuned similarly to Ekstrand's 2012 lenskit based evaluation \cite{ekstrand2012recommenders}.
%%%%%%%%%%%%%%%%%%%%%%
  Since this evaluation was on a slightly different dataset (MovieLens 10M), we performed only minor tuning from these parameters.
  Most notably we found the tuning of the damping parameter used in the baseline recommenders to be too large for this dataset.
  As the damping can have a large effect on baseline quality for new users, we adjusted to a more reasonable damping for this dataset.
  Overall, we did not find our results to be highly sensitive to minor tuning changes, although specific values may change slightly.
%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Introduction}
  % describe new user experience in in recommender systems.
  One of the important problems in recommender systems is the new user experience.
  Most recommenders only have one chance to impress new users.
  If the user doesn't like the system, the user will leave.
  Even if the user stays, how the recommender system behaves for these new users can set the user's expectations for how the system will work in the future.

  % new user experience is important, and here is why.
    % talk about first impressions and user trust
    % How an algorithm behaves the first time a user sees it is important (first impression)
  The user's first impression of the system can be very important in teaching the user to trust the system.
  If the recommendation system does not perform well, the user will not trust its recommendations.
  User trust in recommenders is a complex issue.
  %TODO: re-skim the trust article.

%%%%%%%%%%%%%%%%%%%%%%
  This is especially a concern with recommender systems which rely on large amounts of user information to make personalization decisions.
  When users are new the system will not have much information to personalize the user experience which may lead the user to leave the system.
%%%%%%%%%%%%%%%%%%%%%%

@@

  %TODO: verify these claims.
  %TODO: check for examples of how to write this
  %TODO: the Item-Item algo is ``better'' with just the item mean, not the user item mean. (change is pretty small). 
  %TODO: exstrand's User-User only subtracts the user mean. I havn't tested this, he might have.
  % algorithm is configured as such.
  %TODO: topic sentence.

  % evaluation and code to run these algortihms available at.
  % citations and lenskit info
  Each algorithm was tuned similarly to Ekstrand's 2012 lenskit based evaluation \cite{ekstrand2012recommenders}.
%%%%%%%%%%%%%%%%%%%%%%
  Since this evaluation was on a slightly different dataset (MovieLens 10M), we performed only minor tuning from these parameters.
  Most notably we found the tuning of the damping parameter used in the baseline recommenders to be too large for this dataset.
  As the damping can have a large effect on baseline quality for new users, we adjusted to a more reasonable damping for this dataset.
  Overall, we did not find our results to be highly sensitive to minor tuning changes, although specific values may change slightly.
%%%%%%%%%%%%%%%%%%%%%%
